Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-09-15 2020/OPTIMA/Answers.tex
OPTIMA: clarify definition of uniform convergence

Одновременно с этим результаты численных экспериментов дополнены сравнением предложенного подхода к решению серий задач оптимизации (на примере многокритериальной задачи оптимизации) и генетического алгоритма для решения MCO problems, реализованного в SciPy (see page ...)

@@

\begin{enumerate}
\item p. 3. Apparently, $z_k\neq g_s(x_k ) =:z_{ks}$.
This formula was reformulated.

\item  “To account for the latter” change for “On account of”.
The phrase was replaced.

\item  p. 4. To put more clear the definition (DF) of $Q_i$ (poor grammar usage).

\textbf{Answer}.
The definition was added to the Section 3. See equation (5).

\item  Delete “At that” (???) globally.

@@

@@

@@

>>>>

@@

\begin{enumerate}
\item p. 3. Apparently, $z_k\neq g_s(x_k ) =:z_{ks}$.
\textbf{Answer}.
This formula was reformulated.

\item  “To account for the latter” change for “On account of”.
\textbf{Answer}.
The phrase was replaced.

\item  p. 4. To put more clear the definition (DF) of $Q_i$ (poor grammar usage).
\textbf{Answer}.
The definition was added to the Section 3. See equation (5).

\item  Delete “At that” (???) globally.
\textbf{Answer}.
Deleted.

@@

\textbf{Answer}.
Fixed.

@@

\textbf{Answer}.
Conclusion was rewritten.

@@

\textbf{Answer}.
Definitions and terminology in the Section 3 was corrected.

### 2020-09-15 2020/OPTIMA/optima_paper.tex
OPTIMA: clarify definition of uniform convergence

>>>>

As \cite{BarkalovStrongin2018}, this work aims to formulate a method that will ensure a uniform convergence to the
solutions of all problems in the series. Here and below uniform convergence is taken to
mean proportional decreasing of the distance between the best iteration point and the
global optimizer in all the problems in the series:
\begin{equation}
  \exists \varepsilon > 0: \forall s>1, \forall i,j\in\{1,\dots,q\}\;
    \frac{\Vert \tilde{y_i}(s)^* - y_i*\Vert_\infty}{\Vert \tilde{y_j}(s)^* - y^*_j\Vert_	\infty} \leqslant \varepsilon,
\end{equation}
where \(s\) is the number of step of an optimization method, \(\tilde{y_i}(s)^*\) is the best iteration point
in problem \(i\) from the set (\ref{eq:many_problems}) at the step \(s\).
